---
title: "Cheat sheets"
format: html
editor: visual
toc: true
---

## Introduction

I don't code often enough now to remember cool little tricks that make code both readable and elegant, and when I dip my toes back in, I can get frustrated I'm not working as quickly as I ought to, or fall back on writing lengthy code to brute force. This note is a place to record some of the common operations I might need to do, particularly in the tidyverse, which has changed quite a bit from when I used to use it more regularly - so don't judge me, please!

### Formatting columns using mutate, across, and scales::label_comma (or similar)

Problem: There are multiple columns in a dataframe I want to format in the same way using scales::label\_\*. How can I do this without writing multiple lines within a mutate function call? I would have used mutate_at, but that's superceded.

Solution: Use mutate, and across.

Found on <https://stackoverflow.com/questions/72533524/format-all-numeric-columns-with-comma-to-seprate-the-v>

As noted by the top answer:

> You can use the `scales::label_comma()` function. Note that the format for using this is `scales::label_comma()(x)` since a label function is generated *and then* you call it on your numerical vector.

```{r}
library(dplyr)

df <- tibble(
  Customers = c("babs", "bobs", "pint", "red", "yellow"),
  telex = c(3434323424, 53545322, 43, 35435, 4567),
  manay = c(937387573, 758464938, 7453537384, 624353, 44),
  players = c(96222221, 122134, 223444, 345654, 334)
)
df

df_with_comma <- df |> 
  mutate(across(telex:players, scales::label_comma()))
df_with_comma

# Pass arguments into the label_comma() function to adjust the presentation:
df_with_comma <- df |> 
  mutate(across(telex:players, scales::label_comma(prefix = "🥝", suffix = "🥝")))
df_with_comma


```

## Colour ramping

As taken from Rosa Alonso's analysis

```{r}
my_colours9 <- PrettyCols::prettycols("Coast",
                                      n = 9, # replace with the number of groups in your data
                                      type = 'continuous',
                                      direction = 1) # '1' makes blue first, '-1' makes red first

my_colours6 <- PrettyCols::prettycols("Coast",
                                     n = 6, # replace with the number of groups in your data
                                     type = 'continuous',
                                     direction = 1) # '1' makes blue first, '-1' makes red first

my_colours8 <- PrettyCols::prettycols("Coast",
                                     n = 8, # replace with the number of groups in your data
                                     type = 'continuous',
                                     direction = 1) # '1' makes blue first, '-1' makes red first

my_colours2 <- PrettyCols::prettycols("Coast",
                                      n = 2, # replace with the number of groups in your data
                                      type = 'continuous',
                                      direction = 1) # '1' makes blue first, '-1' makes red first
```
